Building Large-Scale Cross-lingual Knowledge Base from Multi-Encyclopedia

### 2015-06-01 nlpcc/paper.tex
add picture

\textbf{Definition 4:} An ontology is a formal specification of a group of entitie. An ontology can be described as a 6-tuple:
\begin{equation}
    O = <C,I,P,H^C,H^I,H^P>
\end{equation}
where $C$, $I$, $P$ are the sets of concepts, instances, and properties, respectively. $H^C$, $H^I$, $H^P$ represents the hierarchical relationships of concept-concept, concept-instance, instance-property. A Taxonomy$T$ is comprised by $H^C$ and $H^I$, which seperately repesent \emph{SubClassOf} and \emph{InstanceOf} relations.

\textbf{Definition 5:} Given several ontologies generated from various sources, a cross-lingual knowledge base combines them into one. Thus a knowledge base can be defined as 
\begin{equation}
    KB = <O_{i}, CL>
\end{equation}
where O denotes ontologies, CL represents the cross-lingual link set.

\section{Proposed Framework}
Fig. \ref{fig:procedure} presents the whole procedure of our knowledge base building.
\begin{figure}[ht]
    \centerline{\includegraphics[width=1\columnwidth]{fig/procedure}}
    \label{fig:procedure}
    \caption{Procedure of building our cross-lingual knowledge base}
\end{figure}%
We extract information from four sources, Baidu Baike, Hudong Baike, Chinese Wikipedia and English Wikipedia. Considering the different data format of each source, that is, html code page of Baidu and Hudong with different layout, and XML format of Wikipedia dump file, various extractors should be employed. After data parsing, we receive four datasets with concept lists, instance lists, property lists and their relations of each source. Meanwhile, an initial Chinese-English lan-link set is generated, which will be increased by employing a link-discovery method to obtain a larger one. Using the extended language links, we combine the four datasets into one. At last, going through the procedure of taxonomy pruning and data-cleaning, we get a final knowledge base with higher accuracy.

@@

\subsection{Instance Extraction}
\label{sec:ie}
In encyclopedia, an article describes an unique entity in the world. Therefore we can extract an article content as an instance. During the extraction, llustrative or structure-related articles in Wikipedia are deleted, including category list pages and template documentations.

Each instance contains relations with concepts and properties. Take the movie 星际穿越(Interstellar) in Fig.\ref{fig:interstellar} as an example, concepts are assigned according to the category tags below the article page. 美国科幻片(American science fiction films) is a concept of Interstellar. In the meantime, we obtain label property from the article title and abstract property from the first paragraph. Infobox-properties are also acquired via extracting from the infobox in the article. Besides, according to links in the content, we gain the reference $Li(a)$ between the current instance and others, such as 华纳兄弟(Warner Bros.).

After the preprocessing above, we harvest two types of information. One is the characteristics of instance, including $Ti(a)$, $Ab(a)$ of article$a$. The other includes relationships, containing $H^I$ and $H^P$ associate with article$a$.

>>>>

\textbf{Definition 4:} An ontology is a formal specification of a group of entitie. In our work, an ontology is described as a 6-tuple:
\begin{equation}
    O = <C,I,P,H^C,H^I,H^P>
\end{equation}
where $C$, $I$, $P$ are the sets of concepts, instances, and properties, respectively. $H^C$, $H^I$, $H^P$ represents the hierarchical relationships of concept-concept, concept-instance, instance-property. A Taxonomy$T$ is comprised by $H^C$ and $H^I$, which seperately repesent \emph{SubClassOf} and \emph{InstanceOf} relations.

\subsection{Cross-lingual Knowledge Base Building}
A cross-lingual knowledge base is a database conform to a cross-lingual ontology. Taking advantage of language links in $CL$, several mono-ontologies generated from various sources can be merge into one cross-lingual ontology.  Thus a knowledge base can be defined as:
\begin{equation}
    KB = <O_{i}, CL>
\end{equation}
where $O_{i}$ denotes the ith mono-ontology, CL represents the cross-lingual link set.
We build the cross-lingual ontology according to the procedure in Fig. \ref{fig:procedure}
\begin{figure}[ht]
    \centerline{\includegraphics[width=1\columnwidth]{fig/procedure}}
    \label{fig:procedure}
    \caption{Procedure of building our cross-lingual knowledge base}
\end{figure}%
We extract information from four sources, Baidu Baike, Hudong Baike, Chinese Wikipedia and English Wikipedia. Considering the different data format of each source, that is, html code page of Baidu and Hudong with different layout, and XML format of Wikipedia dump file, various extractors should be employed. After data parsing, we receive four datasets with concept lists, instance lists, property lists and their relations of each source. Meanwhile, an initial Chinese-English lan-link set is generated, which will be increased by employing a link-discovery method to obtain a larger one. Using the extended language links, we combine the four datasets into one. At last, going through the procedure of taxonomy pruning and data-cleaning, we get a final knowledge base with higher accuracy.

@@

\subsection{Instance Extraction}
\label{sec:ie}
In encyclopedia, an article describes an unique entity in the world. Therefore we can extract an article content as an instance. During the extraction, illustrative or structure-related articles in Wikipedia are deleted, including category list pages and template documentations.

Each instance contains relations with concepts and properties. Take the movie 星际穿越(Interstellar) in Fig.\ref{fig:interstellar} as an example, concepts are assigned according to the category tags below the article page. 美国科幻片(American science fiction films) is a concept of Interstellar. In the meantime, we obtain label property from the article title and abstract property from the first paragraph. Infobox-properties are acquired via extracting from the infobox in the article. Besides, according to links in the content, we gain the reference $Li(a)$ between the current instance and others, such as 华纳兄弟(Warner Bros.).

After the preprocessing above, we harvest two types of information. One is the characteristics of instance, including $Ti(a)$, $Ab(a)$ of article$a$. The other includes relationships, containing $H^I$ and $H^P$ associated with article $a$.
